---
title: "R Markdown Presentation & Plotly"
author: "Abhinav Agarwal"
date: "8 December 2018"
output: ioslides_presentation
autosize : true
---

## Introduction

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

This is a Coursera project.

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!


## Slide with Code

```{r}
summary(mtcars)
```

## Slide with Plotly

```{r echo=FALSE}
suppressMessages(library(plotly))
suppressMessages(library(ggplot2))
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$am <- factor(mtcars$am, labels = c("Manual", "Automatic"))
g <- ggplot(mtcars, aes(mpg, fill = as.factor(cyl)))+
  geom_histogram(binwidth = 1) + 
  ggtitle("Histogram of miles per gallon from MTCARS") +
  facet_wrap(~am) 
ggplotly(g)
```

## End

Thank You!